---
title: "COMMUNICATIONS"
description: "Talks and posters by Quentin Petitjean (INRAE)"
output: 
  distill::distill_article:
    toc: true
    toc_float: true
    toc_depth: 2
    collapsed: true
    self_contained: false
    code_folding: false
    css:
      - css/GlobalTheme.css
    includes:
      in_header:
        - _others/_headTags.html
---

```{r canonical, include=FALSE, results='asis'}
cat('<link rel="canonical" href="https://qpetitjean.github.io/qpetitjean_distill/communications.html">')
```

```{r SourceFunc, message=FALSE, warning=FALSE, include=FALSE}
# load the function from https://www.jhelvy.com/posts/2021-03-25-customizing-distill-with-htmltools-and-css/
# to create button link redirecting to pdf file
source(file.path("R", "Jp-Helveston-Func.R"))
```
<p class="small-text"><span>&#42;</sup> indicates the person who presented the work.<br/><sup>&#9830;</sup> indicates equal contribution.</p>

# ORAL COMMUNICATIONS

## 2025 
::: {.talks}
`r fontawesome::fa("square-caret-right", fill = "#333333", a11y = "deco")` &ensp; <strong>Q Petitjean</strong>*, Science reproductible : Publier ses données et son code pour une recherche transparente – comment répondre aux attentes des éditeurs. Oral communication (invited speaker) at the <a href='https://jrfrr-2025.sciencesconf.org/'>Journées du Réseau Français de la Recherche Reproductible (JRFRR 2025).</a><br/>`r icon_link(icon = "fa fa-file-pdf", text = "Slides", url = "https://hal.science/hal-05032797v1")`&ensp;`r icon_link(icon = "fa fa-circle-play", text = "Watch the talk (Fr)", url = "https://doi.org/10.60527/ewag-3442")`
:::
## 2024
::: {.talks}
`r fontawesome::fa("square-caret-right", fill = "#333333", a11y = "deco")` &ensp; <strong>Q Petitjean</strong>*, Analyses comportementales en Vidéo-tracking. Oral communication (Workshop animation) at the <a href='https://life.ir.inrae.fr/actualites/jst-life-20242'>Journées scientifiques et techniques de l'IR life 2024.</a>

`r fontawesome::fa("square-caret-right", fill = "#333333", a11y = "deco")` &ensp; <strong>Q Petitjean</strong>*, K Kreutzenberger, J Belliard, L Plichard, B Bourillon, O Dezerald, B Villeneuve, Effect of multiple stressors on migratory fishes: does watershed functioning help better explain population declines? Oral communication at the <a href='https://sfe2-2024.fr/fr'>SFE² meeting 2024.</a>

`r fontawesome::fa("square-caret-right", fill = "#333333", a11y = "deco")` &ensp; <strong>Q Petitjean</strong>*, K Kreutzenberger, J Belliard, L Plichard, B Bourillon, O Dezerald, B Villeneuve, Effets des stress anthropiques sur le déclin des poissons migrateurs : une approche multifactorielle intégrative du fonctionnement des bassins versants. Oral communication at the <a href='https://jilo-2024.sciencesconf.org/'>VI<sup>ème</sup> Journées internationales de limnologie et d'océanographie (JILO 2024).</a>
:::
## 2023
::: {.talks}
`r fontawesome::fa("square-caret-right", fill = "#333333", a11y = "deco")` &ensp; <strong>Q Petitjean</strong>*, M Granada, S Jean, S Manzi, C Veyssiere, A Perrault, M Cousseau, P Laffaille, White J, L Jacquin, Environmentally relevant metal contamination levels affect gut microbiota composition in wild fish populations (<em>Gobio occitaniae</em>). Oral communication at the <a href='https://ecotox-2023.colloque.inrae.fr/'>VIII<sup>ème</sup> Colloque du Réseau Ecotox.</a>
:::
## 2021
::: {.talks}
`r fontawesome::fa("square-caret-right", fill = "#333333", a11y = "deco")` &ensp; <strong>Q Petitjean</strong>*, Variable responses to multiple stressors in a wild freshwater fish: <em>Gobio occitaniae</em>. Oral communication at the <a href='https://www.biologie.uni-hamburg.de/en/forschung/grk2530/'>Department of Biology of the university of Hamburg (RTG 2530).</a> 
:::
## 2019
::: {.talks}
`r fontawesome::fa("square-caret-right", fill = "#333333", a11y = "deco")` &ensp; <strong>Q Petitjean</strong>*, L Jacquin, L Riem, E Rojas, A Perrault, M Cousseau, P Laffaille, S Jean, Variability of responses to multiples stressors in fish: biological level and population matter. Oral communication at the <a href='https://helsinki.setac.org/welcome/'>SETAC Europe 29<sup>th</sup> meeting 2019.</a>
:::
## 2018
::: {.talks}
`r fontawesome::fa("square-caret-right", fill = "#333333", a11y = "deco")` &ensp; <strong>Q Petitjean</strong>*, L Jacquin,  L Riem, E Rojas, A Perrault, M Cousseau, P Laffaille, S Jean, Variability of fish population responses to combined contamination and immune stressors in wild gudgeon. Oral communication at the <a href='https://sfecologie2018.sciencesconf.org/'>SFE² meeting 2018.</a>
:::
## 2017
::: {.talks}
`r fontawesome::fa("square-caret-right", fill = "#333333", a11y = "deco")` &ensp; <strong>Q Petitjean</strong>*, J Côte, S Jean, A Perrault, O Morrisseau, P Laffaille, L Jacquin, Responses of freshwater fish to multiple stressors. Oral communication at the <a href='https://www.freshwatersciences.eu/effs/index.asp?page=SEFS&Id=4'>SEFS meeting 2017.</a>
:::
## 2016
::: {.talks}
`r fontawesome::fa("square-caret-right", fill = "#333333", a11y = "deco")` &ensp; <strong>Q Petitjean</strong>*, A-V Walter-Simonnet, F Choulet, A-L Mariet, P Goncalves, H Laurent, P Rosenthal, A de Vaufleury, F Gimbert, From iron ore to ecotoxicological impacts: One thousand years of manganese history. Oral communication at the <a href='https://ichmet2016.ugent.be/'>ICHMET meeting 2016.</a>
:::
<br/>

# POSTER PRESENTATIONS

## 2024
::: {.poster}
`r fontawesome::fa("square-caret-right", fill = "#333333", a11y = "deco")` &ensp; <strong>Q Petitjean</strong>*<sup>, &#9830;</sup>, S M Dupont<sup>&#9830;</sup>, C Le Picard<sup>&#9830;</sup>, B Bellier<sup>&#9830;</sup>,  H Sentenac<sup>&#9830;</sup>, S Bancel<sup>&#9830;</sup>, E FUENTES<sup>&#9830;</sup>, Young ecotoxicologist group (yeg), le groupe des jeunes ecotoxicologues francophones. Poster presentation at the <a href='https://asso-sefa.fr/colloque-de-la-sefa'>French SEFA meeting 2024.</a><br/>`r icon_link(icon = "fa fa-file-pdf", text = "Poster", url ="Posters/Petitjeanetal-YEG-POSTER.pdf")`
:::
## 2023
::: {.poster}
`r fontawesome::fa("square-caret-right", fill = "#333333", a11y = "deco")` &ensp; <strong>Q Petitjean</strong>*, S Lartigue, M Cointe, R LeClech,  M Ion Scotta, N Ris, L Van Oudenhove, V Calcagno, MoveR: a package for the visualization and analysis of video-tracking data in R. Poster presentation at the <a href='https://entomo2023.sciencesconf.org/'>43èmes journées des Entomophagistes.</a><br/>`r icon_link(icon = "fa fa-file-pdf", text = "Poster", url ="Posters/Petitjeanetal-MOVER-POSTER.pdf")`
:::
## 2019
::: {.poster}
`r fontawesome::fa("square-caret-right", fill = "#333333", a11y = "deco")` &ensp; M Pitout*, <strong>Q Petitjean</strong>, A Perrault, M Cousseau, P Laffaille, L Jacquin, S Jean, Physiological and transcriptomic responses to metal contamination and immune challenge in gudgeon. Poster presentation at the <a href='https://eb2019.sciencesconf.org/'>E&B meeting 2019.</a>
:::
## 2018
::: {.poster}
`r fontawesome::fa("square-caret-right", fill = "#333333", a11y = "deco")` &ensp; <strong>Q Petitjean</strong>*, S Jean, J Côte, A Lamarins, A Perrault, P Laffaille, L Jacquin, Responses to combined temperature and immune stressors in wild gudgeon. Poster presentation at the <a href='https://sfecologie2018.sciencesconf.org/'>SFE² meeting 2018.</a><br/>`r icon_link(icon = "fa fa-file-pdf", text = "Poster", url ="Posters/Petitjeanetal-TempImmStress-POSTER.pdf")`
:::
## 2017
::: {.poster}
`r fontawesome::fa("square-caret-right", fill = "#333333", a11y = "deco")` &ensp; <strong>Q Petitjean</strong>*, J Côte, L Jacquin, A Perrault, O Morrisseau, P Laffaille, S Jean, Responses of freshwater fish to multiple stressors. Poster presentation at the FEE meeting 2017.
:::
## 2016
::: {.poster}
`r fontawesome::fa("square-caret-right", fill = "#333333", a11y = "deco")` &ensp; <strong>Q Petitjean</strong>*, A-V Walter-Simonnet, F Choulet, A-L Mariet, P Goncalves, H Laurent, P Rosenthal, A de Vaufleury, F Gimbert, Impacts de la pr&eacute;sence de d&eacute;chets sid&eacute;rurgiques anciens sur la contamination des sols en m&eacute;taux. Poster presentation at the <a href='https://asso-sefa.fr/colloque-de-la-sefa'>French SEFA meeting 2016.</a><br/>`r icon_link(icon = "fa fa-file-pdf", text = "Poster", url ="Posters/Petitjeanetal-MineWastes-POSTER.pdf")`
:::
<br/><br/>

<nav>
  <a href="/qpetitjean_distill/news.html" style="color:rgba(20, 130, 125, 1); font-style: italic; border-bottom: 0px; text-decoration: none; margin-right: 0px; margin-left: 0px;">News</a> |
  <a href="/qpetitjean_distill/publications.html" style="color:rgba(20, 130, 125, 1); font-style: italic; border-bottom: 0px; text-decoration: none; margin-right: 0px; margin-left: 0px;">Publications</a> |
  <a href="/qpetitjean_distill/communications.html" style="color:rgba(20, 130, 125, 1); font-style: italic; border-bottom: 0px; text-decoration: none; margin-right: 0px; margin-left: 0px;">Communications</a> |
  <a href="/qpetitjean_distill/cv.html" style="color:rgba(20, 130, 125, 1); font-style: italic; border-bottom: 0px; text-decoration: none; margin-right: 0px; margin-left: 0px;">Curriculum Vitae </a>
</nav>
<html lang="en">